### 2017-11-14 submission/manuscript.Rmd
add Will's Declaration changes

Ethics approval and informed consent for each of the studies used is mentioned in the respective manuscript used in this meta-analysis.

@@

A detailed and reporducible description of how the data were processed and analyzed for each study can be found at https://github.com/SchlossLab/Sze_CRCMetaAnalysis_Microbiome_2017. Raw sequences can be downloaded from the SRA in most cases and can be found in the respective studies batch file in the GitHub repo or within the original publication. When sequences were not publicly available contacting the corresponding author for raw sequences needs to be undertaken.

@@

MAS is supported by a CIHR fellowship and a University of Michigan PTSP fellowship grant.

@@

The authors would like to thank all the study participants who were apart of each of the individual studies uitlized. We would also like to thank each of the study authors for making their data available for use. Finally we would like to thank the members of the Schloss lab for valuable feed back and proof reading during the formulation of this manuscript.

>>>>

Ethics approval and informed consent for each of the studies used is mentioned in the respective manuscripts used in this meta-analysis.

@@

A detailed and reproducible description of how the data were processed and analyzed for each study can be found at https://github.com/SchlossLab/Sze_CRCMetaAnalysis_Microbiome_2017. Raw sequences can be downloaded from the SRA in most cases and can be found in the respective studies batch file in the GitHub repository or within the original publication. For instances when sequences are not publicly available, they may be accessed by contacting the corresponding authors from whence the data came.

@@

MAS is supported by a Candian Institute of Health Research fellowship and a University of Michigan Postdoctoral Translational Scholar Program grant.

@@

The authors would like to thank all the study participants who were a part of each of the individual studies uitlized. We would also like to thank each of the study authors for making their data available for use. Finally we would like to thank the members of the Schloss lab for valuable feed back and proof reading during the formulation of this manuscript.

### 2017-11-14 submission/manuscript.tex
add Will's Declaration changes

A detailed and reporducible description of how the data were processed
and analyzed for each study can be found at
\url{https://github.com/SchlossLab/Sze_CRCMetaAnalysis_Microbiome_2017}.
Raw sequences can be downloaded from the SRA in most cases and can be
found in the respective studies batch file in the GitHub repo or within
the original publication. When sequences were not publicly available
contacting the corresponding author for raw sequences needs to be
undertaken.

>>>>

A detailed and reproducible description of how the data were processed
and analyzed for each study can be found at
\url{https://github.com/SchlossLab/Sze_CRCMetaAnalysis_Microbiome_2017}.
Raw sequences can be downloaded from the SRA in most cases and can be
found in the respective studies batch file in the GitHub repository or
within the original publication. For instances when sequences are not
publicly available, they may be accessed by contacting the corresponding
authors from whence the data came.
